Data Cleaning

### 2025-12-09 Data Cleaning.Rmd
updated multinomial regression model

multi_recipe1 <- recipe(FeCl_change ~ mean_pH + mean_Temp, data = df_train) |>
  step_normalize(all_numeric_predictors()) |>
  step_dummy(all_nominal_predictors())

@@

accuracy_result <- metrics(df_pred_class, truth = FeCl_change, estimate = .pred_class)
confusion_matrix <- conf_mat(df_pred_class, truth = FeCl_change, estimate = .pred_class)

@@

library(broom)
library(dplyr)
library(knitr)    # For kable()
library(kableExtra) # For extra formatting

# 1. Extract the model fit object
fit_engine <- multi_fit |> extract_fit_engine()

# 2. Tidy the results using the broom package
# The tidy function converts the coefficient matrix into a clean data frame.
tidy_coeffs <- tidy(fit_engine)

# 3. Format the table using kable/kableExtra for display
tidy_coeffs |>
  # Round all numeric columns for cleaner display
  mutate(across(where(is.numeric), ~ round(., 4))) |>

  # Rename columns for clarity (optional, but helpful)
  rename(
    Category = y.level,
    Predictor = term,
    Coefficient = estimate,
    Std_Error = std.error,
    Z_Value = statistic,
    P_Value = p.value
  ) |>

  # Create a nicely formatted Markdown table
  knitr::kable("markdown")
  # OR use kableExtra for more styling options (e.g., HTML/PDF output)
  # kableExtra::kbl(format = "html") |>
  # kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
multi_fit |> extract_fit_engine() |> tibble()
```

>>>>

multi_recipe1 <- recipe(FeCl_change ~ mean_Temp + Temp_lag1 + Temp_lag2 + mean_pH + pH_lag1 + pH_lag2 + mean_Conductivity + Cond_lag1 + Cond_lag2, data = df_train) |>
  step_normalize(all_numeric_predictors()) |>
  step_dummy(all_nominal_predictors())

@@

accuracy_result <- metrics(df_pred_class, truth = FeCl_change, estimate = .pred_class) |> 
  filter(.metric == "accuracy")
confusion_matrix <- conf_mat(df_pred_class, truth = FeCl_change, estimate = .pred_class)

@@

multi_fit |> extract_fit_engine()

## NOTES
# turbidity is highly variable and does not help
